Hazelnut: A Bidirectionally Typed \\ Structure Editor Calculus

### 2016-10-06 hazelnut-popl17.tex
if we're gonna be faux french, we might as well spell it right

\usepackage{joshuadunfield}
\usepackage{llproof}
\usepackage{rulelinks}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newenvironment{proof-sketch}{\noindent{\emph{Proof Sketch.}}}{\qed}
\makeatletter

@@

This paper defines Hazelnut, a {structure editor} based on a small
bidirectionally typed lambda calculus extended with \emph{holes} and
a \emph{cursor} (\emph{ala} Huet's zipper.) Hazelnut goes one step beyond
syntactic well-formedness: its {edit actions} operate over statically
meaningful (i.e. well-typed) terms.  Na\"ively, this prohibition on
ill-typed edit states would force the programmer to construct terms in a
rigid ``outside-in'' manner. To avoid this problem, the {action semantics}
automatically places terms assigned a type that is inconsistent with the
expected type {inside} a {hole}. This safely defers the type consistency
check until the term inside the hole is \emph{finished}.

>>>>

\usepackage{joshuadunfield}
\usepackage{llproof}
\usepackage{rulelinks}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newenvironment{proof-sketch}{\noindent{\emph{Proof Sketch.}}}{\qed}
\makeatletter

@@

This paper defines Hazelnut, a {structure editor} based on a small
bidirectionally typed lambda calculus extended with \emph{holes} and
a \emph{cursor} (\emph{\`{a} la} Huet's zipper.) Hazelnut goes one step beyond
syntactic well-formedness: its {edit actions} operate over statically
meaningful (i.e. well-typed) terms.  Na\"ively, this prohibition on
ill-typed edit states would force the programmer to construct terms in a
rigid ``outside-in'' manner. To avoid this problem, the {action semantics}
automatically places terms assigned a type that is inconsistent with the
expected type {inside} a {hole}. This safely defers the type consistency
check until the term inside the hole is \emph{finished}.
